DynaProg for Scala

### 2013-01-21 docs/report/benchmarks.tex
Nits, small improvement for Scala.

\documentclass[11pt]{article}
\input{inc/style.sty}
\begin{document}

@@

\def\hdr#1#2{\begin{minipage}{3.5cm} {\bf #1} \\[-2pt] \footnotesize #2 \vspace{6pt} \end{minipage}}
\begin{table}[H]\begin{center}{\small\begin{tabular}{llrrrrrrrr}\toprule
& \normalsize\bf Matrix dimension & \normalsize\bf 128 & \normalsize\bf 256 & \normalsize\bf 512 & \normalsize\bf 1024 & \normalsize\bf 2048 & \normalsize\bf 4096 & \normalsize\bf 8192 \\
\midrule \multirow{4}{*}{\rotatebox{90}{\normalsize\bf CPU $\qquad$}}
& \hdr{DynaProg}{Scala version}
	& 0.247		& 2.048		& 16.657		& 134.207	& 1101.134	&  			& 		 \\
& \hdr{Optimized}{C, single thread}
	& 0.001		& 0.008		& 0.078		& 1.179		& 19.811		& 206.556	& 2010.485 \\
& \hdr{GAPC}{\cite{gapc_thesis}, C, single thread}
	& 			& 			& 			& 			& 			& 			& 		 \\
& \hdr{ADP Fusion}{\cite{adp_fusion}}
	& 			& 			& 			& 			& 			& 			& 		 \\[-2pt]
\midrule \multirow{4}{*}{\rotatebox{90}{\normalsize\bf GPU $\qquad\quad$}}
& \hdr{DynaProg}{CUDA version}
	& 0.028		& 0.046		& 0.129		& 0.348		& 1.685		& 10.308		& 71.215 \\
& \hdr{Optimized}{CUDA, 64-bit}
	& 0.011		& 0.020		& 0.074		& 0.315		& 1.651		& 10.354		& 72.376 \\
% 32-bit &&		&			&			& 0.316		& 1.427		& 8.841		& 62.064
& \hdr{ATLP}{\cite{gpu_atlp}, rescaled results$^{(1)}$}
	& 0.170		& 0.199		& 0.227		& 0.397		& 1.335		& 7.299 		& - \\
\\[-10pt] \bottomrule\end{tabular}}\end{center}
\caption{Running time of matrix chain multiplication (in seconds)}\end{table}

@@

\subsection{Smith-Watermann}
% CPU: DynaProg(Scala), hand optimized C, GAPC and ADPFusion
% GPU: DynaProg(CUDA), hand optimized CUDA, CUDAlign
XXX: to compare appropriately either use 3 matrices or constant gap penalty
XXX: move toward use of 3 matrices

\def\hdr#1#2{\begin{minipage}{3.5cm} {\bf #1} \\[-2pt] \footnotesize #2 \vspace{6pt} \end{minipage}}
\begin{table}[H]\begin{center}{\small\begin{tabular}{llrrrrrrrr}\toprule
& \normalsize\bf Matrix dimension & \normalsize\bf 128 & \normalsize\bf 256 & \normalsize\bf 512 & \normalsize\bf 1024 & \normalsize\bf 2048 & \normalsize\bf 4096 & \normalsize\bf 8192 \\
\midrule \multirow{4}{*}{\rotatebox{90}{\normalsize\bf CPU $\qquad$}}
& \hdr{DynaProg}{Scala version}
	& 0.115		& 0.438		& 1.743		& 7.864		& 32.788		& 139.309	& $^{(1)}\infty$ \\
& \hdr{Optimized}{C, single thread}
	& <0.001		& <0.001		& 0.002		& 0.009		& 0.042		& 0.171		& 0.706 \\
& \hdr{GAPC}{\cite{gapc_thesis}, C, single thread}
	& 			& 			& 			& 			& 			& 			& 		 \\
& \hdr{ADP Fusion}{\cite{adp_fusion}}
	& 			& 			& 			& 			& 			& 			& 		 \\[-2pt]
\midrule \multirow{4}{*}{\rotatebox{90}{\normalsize\bf GPU $\qquad$}}
& \hdr{DynaProg}{CUDA version}
	& 0.031		& 0.037		& 0.047		& 0.068		& 0.116		& 0.202		& $^{(2)}$3.226 \\
& \hdr{Optimized}{CUDA, 64-bit}
	& 0.002		& 0.004		& 0.004		& 0.007		& 0.024		& 0.070		& 0.270 \\
& \hdr{CUDAlign}{\cite{swat_linear}, version 2.0}
	& 			& 			& 			& 			& 			& 			& 		 \\
\\[-10pt] \bottomrule\end{tabular}}\end{center}
\caption{Running time of Smith-Waterman (in seconds)}\end{table}

@@

X: java.lang.OutOfMemoryError: GC overhead limit exceeded

@@

XXX: continue benchmarking here
}
\begin{table}[H]\begin{center}\begin{tabular}{lrrrrrr} \toprule
Matrix size			& 1024	& 2048	& 4096	& 8192 \\
Splits				& 1		& 8		& 64		& 512 \\ \midrule
Analysis				& 0.007	& 0.007	& 0.007	& 0.007 \\
Code generation		& 0.071	& 0.072	& 0.073	& 0.071 \\
C/CUDA compilation	& 3.025	& 1.836	& 1.832	& 1.841 \\
Scala compilation		& 1.837	& 1.853	& 1.830	& 1.767 \\ \midrule
- JNI read				& 0.027	& 0.028	& 0.029	& 0.058 \\
- CUDA compute		& 0.868	& 3.378	& 19.782	& 139.697 \\
- CUDA backtrack		& 0.009	& 0.012	& 0.023	& 0.045 \\
- JNI output			& 0.005	& 0.009	& 0.018	& 0.032 \\
Total execution			& 0.915	& 3.432	& 19.860	& 139.846 \\ \bottomrule
\end{tabular}\end{center}\caption{Preliminary results for MatrixMultGen}\end{table}

@@

\end{document}

>>>>

%\documentclass[11pt]{article}\input{inc/style.sty}\begin{document}

@@

\def\hdr#1#2{\begin{minipage}{3.5cm} {\bf #1} \\[-2pt] \footnotesize #2 \vspace{6pt} \end{minipage}}
\begin{table}[H]\begin{center}{\small\begin{tabular}{llrrrrrrrr}\toprule
& \normalsize\bf Matrix dimension & \normalsize\bf 128 & \normalsize\bf 256 & \normalsize\bf 512 & \normalsize\bf 1024 & \normalsize\bf 2048 & \normalsize\bf 4096 & \normalsize\bf 8192 \\
\midrule \multirow{4}{*}{\rotatebox{90}{\normalsize\bf CPU $\qquad$}}
& \hdr{DynaProg}{Scala version}
	& 0.247		& 2.048		& 16.657		& 134.207	& 1101.134	&  			& 		 \\
& \hdr{Optimized}{C, single thread}
	& 0.001		& 0.008		& 0.078		& 1.179		& 19.811		& 206.556	& 2010.485 \\
& \hdr{GAPC}{\cite{gapc_thesis}, C, single thread}
	& 0.012		& 0.050		& 0.348		& 2.822		& 25.163		& 224.704	& 		 \\
& \hdr{ADP Fusion}{\cite{adp_fusion}}
	& 			& 			& 			& 			& 			& 			& 		 \\[-2pt]
\midrule \multirow{4}{*}{\rotatebox{90}{\normalsize\bf GPU $\qquad\quad$}}
& \hdr{DynaProg}{CUDA version}
	& 0.028		& 0.046		& 0.129		& 0.348		& 1.685		& 10.308		& 71.215 \\
& \hdr{Optimized}{CUDA, 64-bit}
	& 0.011		& 0.020		& 0.074		& 0.315		& 1.651		& 10.354		& 72.376 \\
% 32-bit &&		&			&			& 0.316		& 1.427		& 8.841		& 62.064
& \hdr{ATLP}{\cite{gpu_atlp}, rescaled results$^{(1)}$}
	& 0.170		& 0.199		& 0.227		& 0.397		& 1.335		& 7.299 		& --- \\
\\[-10pt] \bottomrule\end{tabular}}\end{center}
\caption{Running time of matrix chain multiplication (in seconds)}\end{table}

@@

\subsection{Smith-Watermann}
% CPU: DynaProg(Scala), hand optimized C, GAPC and ADPFusion
% GPU: DynaProg(CUDA), hand optimized CUDA, CUDAlign
To maintain a fair comparison with other implementation, we use affine gap penalty variant of the Smith-Waterman algorithm. For that, we need to encode it with 3 tabulations in our grammar, whereas domain-specific application can leverage the knowledge that two of these matrices can be removed by storing appropriate information in the computation wavefront (\S\ref{calc_simplifications}).
%XXX: to compare appropriately either use 3 matrices or constant gap penalty

\def\hdr#1#2{\begin{minipage}{3.5cm} {\bf #1} \\[-2pt] \footnotesize #2 \vspace{6pt} \end{minipage}}
\begin{table}[H]\begin{center}{\small\begin{tabular}{llrrrrrrrr}\toprule
& \normalsize\bf Matrix dimension & \normalsize\bf 128 & \normalsize\bf 256 & \normalsize\bf 512 & \normalsize\bf 1024 & \normalsize\bf 2048 & \normalsize\bf 4096 & \normalsize\bf 8192 \\
\midrule \multirow{4}{*}{\rotatebox{90}{\normalsize\bf CPU $\qquad$}}
& \hdr{DynaProg}{Scala version}
	& 0.115		& 0.438		& 1.743		& 7.864		& 32.788		& 139.309	& $^{(1)}\infty$ \\
& \hdr{Optimized}{C, single thread}
	& <0.001		& <0.001		& 0.002		& 0.009		& 0.042		& 0.171		& 0.706 \\
& \hdr{GAPC}{\cite{gapc_thesis}, C, single thread}
	& 			& 			& 			& 			& 			& 			& 		 \\
& \hdr{ADP Fusion}{\cite{adp_fusion}}
	& 			& 			& 			& 			& 			& 			& 		 \\[-2pt]
\midrule \multirow{4}{*}{\rotatebox{90}{\normalsize\bf GPU $\qquad$}}
& \hdr{DynaProg}{CUDA version}
	& 0.031		& 0.037		& 0.047		& 0.068		& 0.116		& 0.202		& $^{(2)}$3.226 \\
& \hdr{Optimized}{CUDA, 64-bit}
	& 0.002		& 0.004		& 0.004		& 0.007		& 0.024		& 0.070		& 0.270 \\
& \hdr{CUDAlign}{\cite{swat_linear}, version 2.0}
	& 0.011		& 0.011		& 0.011		& 0.011		& 0.011		& 0.011		& 0.012 \\
\\[-10pt] \bottomrule\end{tabular}}\end{center}
\caption{Running time of Smith-Waterman (in seconds)}\end{table}

@@

@@

XXX: continue benchmarking here
}

@@

%\end{document}
